Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-17 CMSAC_presentation/CMSAC_reveal_js.qmd
reorder pics

::: fragment
```{r}
knitr::include_graphics("five_rec_league_men_playing_basketball.png")
```
:::

@@

::: fragment
```{r}
knitr::include_graphics("five_babies_playing_basketball.png")

```
:::
:::::::

>>>>

::: fragment
```{r}
knitr::include_graphics("five_babies_playing_basketball.png")
```
:::

@@

::: fragment
```{r}
knitr::include_graphics("five_rec_league_men_playing_basketball.png")
```
:::
:::::::
